Basic Model formulation

### 2015-01-29 documentation/model_formulation.Rmd
develop nullmodel for cellular automata and ODE

```{r, echo=FALSE}
par(mar = c(4,4,2,4))
plot(rho,  with(parms,  r * b *  ( 1 - (rho / K)) / (1 - rho) ) , ylab = "individual growth on empty cells", type = "l", ylim = c(0,2.5), las = 1, yaxs = "i")

@@

Running this in a timeseries of 150 years yields

```{r, echo = FALSE}

@@

nullmodel <- runCA(0.9, parms, delta = 0.2, t_max = 150, t_min = 100, t_eval = 50, isstable = 0.0001, saveeach = 5)

@@

lines(ODEnullmodel, lty = 3)

#animateCA(nullmodel, "ca_nullmodel.gif")

>>>>

```{r, echo=FALSE}
par(mar = c(4,4,2,4))
plot(rho,  with(parms,  r * b * rho * ( 1 - (rho / K)) / (1 - rho) ) , ylab = "individual growth on empty cells", type = "l", ylim = c(0,2.5), las = 1, yaxs = "i")

@@

Running this on a 100 x 100 grid of cells in a timeseries of 150 years yields (dashed line: ODE prediction as reference)

```{r, echo = FALSE, warning = FALSE}

@@

nullmodel <- runCA(0.9, parms, delta = 0.2, t_max = 150, t_min = 100, t_eval = 50, isstable = 0.0001, saveeach = 1)

@@

lines(ODEnullmodel, lty = 3)
```

And the animated lattice would look like this:
```{r, eval = FALSE, echo = FALSE, warning = FALSE}
animateCA(nullmodel, "ca_nullmodel.gif")
```
![](ca_nullmodel.gif)
